Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd

In an ideal world, where a $100k in funds and all necessary resources could be obtained from a neutral source for the purpose of polling the population, the idealized methodology for a survey that aims to forecast the results of the US election should be one that uses quota sampling and the probability proportionate to size method to target the states of interest specifically. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past eight elections [@blueredstate]. Out of the 51 states, there are 20 states which voted for the same party each time in the past nine elections and therefore there is a high probability that the pattern will be upheld with this year's election [@blueredstate]. On the other end of the spectrum, there are seven states which have voted for each party three of more times within the last nine elections——these would be the states of greater interest to us [@blueredstate].

Using the non-probability sampling method of quota sampling, these swing states will first be selected. This targetted sampling process allows us to focus our polling efforts on gathering more data from the areas where there is higher uncertainty, but the tradeoff is bias is easily introduced with the assumptions we are making, potentially impacting the accuracy of our forecast [@quotasampling]. This means that more work is required to adjust for these biases while also minimizing the inflation of variance [@quotasamping].

@@

- questions (wording, order, options)
- treatment of non-response
- offer of incentive

After analysis of poll responses, the votes of the consistent states should be added back into consideration before making the final forecast for election results.

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, such as Survey Monkey, the question order would be randomized when being presented to different respondents with the Question Randomization feature [@surveymonkey]. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].

>>>>

In an ideal world, where a $100k in funds and all necessary resources could be obtained from a neutral source for the purpose of polling the population, the idealized methodology for a survey that aims to forecast the results of the US election should be one that uses quota sampling and the probability proportionate to size method to target the states of interest specifically. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past eight elections [@blueredstate]. Out of the 51 states, there are 20 states which voted for the same party each time in the past nine elections and therefore there is a high probability that the pattern will be upheld with this year's election [@blueredstate]. On the other end of the spectrum, there are seven states which have voted for each party three of more times within the last nine elections—these would be the states of greater interest to us [@blueredstate].

Using the non-probability sampling method of quota sampling, these swing states will first be selected. This targetted sampling process allows us to focus our polling efforts on gathering more data from the areas where there is higher uncertainty, but the tradeoff is bias is easily introduced with the assumptions we are making, potentially impacting the accuracy of our forecast [@quotasampling]. This means that more work is required to adjust for these biases while also minimizing the inflation of variance [@quotasampling].

@@

The wording of questions should be straightforward and easy to understand, minimizing error in measurement caused by misinterpretation of questions. The question should also be asked neutrally, without leading participants to any particular response. Likert scales, including an option for “don’t know”, should be used whenever possible for ease and consistency of participant understanding. As well, keeping questions and answer options simple minimizes the burden placed on participants, which reduces the attrition caused by participants losing interest in the poll [@citeTB]. The “don’t know” option is also effective in helping reduce the decision difficulty to certain participants who are truly unsure. Before officially deploying the survey with our selected sample, it first needs to be tested to catch ambiguous or other poorly phrased questions [@citeTB]. To encourage participation in this research, a financial incentive should be offered for full completion of the poll. Displaying the progress bar and indicating the survey length at the very beginning also helps encourage participants to complete the full questionnaire. Our poll would also be submitted to the appropriate ethics review boards to increase confidence in our methodology.

Some information of interest to us, such as voting history and racial identification, is already included in the registered voter file, so these questions can be excluded from the poll itself [@voterfiledata]. After analysis of poll responses, the votes of the historically consistent states should be added back into consideration before making the final forecast for election results.

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, the question order would be randomized when being presented to different respondents, with consideration for related questions must be kept together. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].
